% \documentclass[jounal, onecolumn]{IEEEtran}
\PassOptionsToPackage{table}{xcolor}
\documentclass[pdflatex,sn-mathphys-num]{sn-jnl}


\usepackage{graphicx} % Required for inserting images
\usepackage{manyfoot}
\usepackage{amsmath} 
\usepackage{comment}
\usepackage{amssymb}
% \usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{algpseudocode}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage{multirow}

% sn-jnl loads hyperref internally.
\usepackage[most]{tcolorbox}
\usepackage{float}
\usepackage{ulem}
\usepackage{xcolor}
\usepackage{subcaption}
\usepackage{stmaryrd}
% sn-jnl loads natbib; loading cite as in the IEEE draft breaks citations.
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{makecell}
% package
\usepackage{tikz}
\usepackage{array}
\usepackage{setspace}
\usepackage{pifont}

\newcommand{\cmark}{\ding{51}}
\newcommand{\xmark}{\ding{55}}
\newcommand{\omark}{\ding{108}}

\definecolor{darkblue}{rgb}{0.15,0.15,0.55}
\definecolor{lightgrey}{rgb}{0.75,0.75,0.75}
\newcommand{\qedm}{\hfill $\square$}
\DeclareUnicodeCharacter{25B3}{\ensuremath{\triangle}}
\newcommand\ny[1]{{\color{magenta}{#1}}}
\newcommand\sj[1]{{\color{violet}{#1}}}
\newcommand\sh[1]{{\color{orange}{#1}}}
\newcommand\gy[1]{{\color{purple}{#1}}}
\newcommand\cp[1]{{\color{blue}{#1}}}
\newcommand\jh[1]{{\color{green}{#1}}}

\hyphenation{op-tical net-works semi-conduc-tor}
\raggedbottom

 \begin{document}
 
\title{BRL Architecture}

\author*[1]{\fnm{Changmin}~\sur{Park}}\email{cmp9877@gmail.com}
\author[1]{\fnm{Seongah}~\sur{Park}}\email{ppseongah@gmail.com}
\author[1]{\fnm{Nayoung}~\sur{Kim}}
\author[1]{\fnm{Sungjin}~\sur{Park}}
\author[1]{\fnm{Geonyeong}~\sur{Ko}}
\author[2]{\fnm{Junho}~\sur{Lee}}
\author[2]{\fnm{Changjoo}~\sur{Nam}}

\affil*[1]{\orgname{Sogang University}, \country{Republic of Korea}}
\affil[2]{\orgname{Institution2}}



% \author{Changmin~Park,
%         Seongah~Park,
%         Junho~Lee,
%         Nayoung~Kim,
%         Sungjin~Park,
%         Gungyoung~Go, % 고건영
%         and~Changjoo~Nam% <-this % stops a space
% \thanks{M. Shell was with the Department
% of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta,
% GA, 30332 USA e-mail: (see http://www.michaelshell.org/contact.html).}% <-this % stops a space
% \thanks{J. Doe and J. Doe are with Anonymous University.}% <-this % stops a space
% \thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}


\abstract{In this paper, we present a knowledge-based POMDP framework that enables robots to selectively request human feedback under uncertainty. While modern robotic systems achieve strong autonomy, they still fail due to perception errors, execution failures, and environmental changes, often requiring continuous human supervision. We model decision making as a POMDP over a symbolic knowledge base, where uncertainty is quantified using the entropy of a belief over possible world states to determine when to query. The system also determines what to query by selecting informative queries that reduce ambiguity between competing hypotheses. We evaluate the proposed method in both a simulated waste sorting task and a real-world tomato harvesting task. Results show that our approach maintains task success rates comparable to full supervision while significantly reducing the number of queries, and user studies confirm reduced cognitive workload during interaction.}

\keywords{robotic system, planning under uncertainty, human-robot interaction}

\maketitle

\input{section/01_intro}
\input{section/02_related}
\input{section/03_preliminaries}
\input{section/04_method}
\input{section/05_exp_setting}
\input{section/05_exp_system}
\input{section/05_exp_user}
\input{section/06_conclusion}


\section*{Acknowledgement}
% \vspace{-5pt}
This research was supported in part by the National Research Foundation of Korea (NRF) grant funded by the Korea government (MSIT)(No. RS-2024-00461583) and the National Research Foundation of Korea (NRF) grant funded by the Korea government (MSIT) (No. RS-2024-00411007).


% sn-jnl selects the bibliography style from the class option.
\bibliography{IEEEabrv, ref}


\begin{appendices}
\input{appendix/00_appx_content}
\input{appendix/01_algorithms.tex}
\input{appendix/02_detailedEXP.tex}
\input{appendix/03_exp.tex}
\input{appendix/04_user_study.tex}
\end{appendices}


\end{document}
