\section{Preliminaries}
\label{sec:preliminaries}

\subsection{Symbolic Planning}

Let $\mathcal{F}$ be a finite set of symbolic atoms. A symbolic state is a subset $s \subseteq \mathcal{F}$. An action $a \in \mathcal{A}$ is defined by preconditions, add effects, and delete effects:
\[
a = \langle \mathrm{pre}(a), \mathrm{add}(a), \mathrm{del}(a) \rangle .
\]
The action is applicable in state $s$ if $\mathrm{pre}(a) \subseteq s$. Applying $a$ produces
\[
s' = (s \setminus \mathrm{del}(a)) \cup \mathrm{add}(a).
\]
In robot domains, symbolic actions are grounded to executable skills such as detecting an object, navigating to a location, picking an object, placing an object, scanning a tomato, or discarding an item.

\subsection{POMDPs and POMCP}

A POMDP is a tuple $\mathcal{M}=\langle \mathcal{S},\mathcal{A},T,R,\Omega,O,\gamma\rangle$, where $\mathcal{S}$ is the state space, $\mathcal{A}$ the action space, $T(s'|s,a)$ the transition model, $R(s,a)$ the reward function, $\Omega$ the observation space, $O(o|s',a)$ the observation model, and $\gamma$ the discount factor. Since the state is not directly observed, the robot maintains a belief $b(s)$ over states. After action $a$ and observation $o$, the Bayesian belief update is
\begin{equation}
b'(s') = \eta O(o|s',a)\sum_{s \in \mathcal{S}}T(s'|s,a)b(s),
\label{eq:bayes}
\end{equation}
where $\eta$ is a normalizer.

POMCP approximates online POMDP planning through Monte Carlo tree search over histories~\cite{silver2010monte}. Each history node stores sampled particles and action values. During simulation, actions are selected using an upper-confidence rule,
\begin{equation}
a^* = \arg\max_a \left[V(ha) + c\sqrt{\frac{\log N(h)}{N(ha)}}\right],
\label{eq:ucb}
\end{equation}
where $V(ha)$ is the estimated value of taking action $a$ after history $h$, $N(h)$ is the visit count of the history, and $N(ha)$ is the visit count of the action branch.

\subsection{Human Feedback as Information}

We treat a human response as an observation over a symbolic hypothesis. A hypothesis is a literal $q \in \mathcal{F}$ whose truth value is uncertain in the current belief. A query asks the human to verify $q$, producing an answer $y \in \{\texttt{true},\texttt{false}\}$. The answer filters the belief by retaining states consistent with $y$. Thus, a query affects future planning by changing the posterior over symbolic worlds.
