\PassOptionsToPackage{table}{xcolor}
\documentclass[journal]{IEEEtran}

\usepackage{cite}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{comment}
\usepackage{algpseudocode}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage{multirow}
\usepackage[most]{tcolorbox}
\usepackage{float}
\usepackage{ulem}
\usepackage{xcolor}
\usepackage{subcaption}
\usepackage{stmaryrd}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage{tikz}
\usepackage{array}
\usepackage{setspace}
\usepackage{pifont}

\newcommand{\cmark}{\ding{51}}
\newcommand{\xmark}{\ding{55}}
\newcommand{\omark}{\ding{108}}

\definecolor{darkblue}{rgb}{0.15,0.15,0.55}
\definecolor{lightgrey}{rgb}{0.75,0.75,0.75}
\newcommand{\qedm}{\hfill $\square$}
\DeclareUnicodeCharacter{25B3}{\ensuremath{\triangle}}
\newcommand\ny[1]{{\color{magenta}{#1}}}
\newcommand\sj[1]{{\color{violet}{#1}}}
\newcommand\sh[1]{{\color{orange}{#1}}}
\newcommand\gy[1]{{\color{purple}{#1}}}
\newcommand\cp[1]{{\color{blue}{#1}}}
\newcommand\jh[1]{{\color{green}{#1}}}

\hyphenation{op-tical net-works semi-conduc-tor}
\raggedbottom

\begin{document}

\title{BRL Architecture}

\author{Changmin~Park,
        Seongah~Park,
        Nayoung~Kim,
        Sungjin~Park,
        Geonyeong~Ko,
        Junho~Lee,
        and~Changjoo~Nam%
\thanks{Changmin Park, Seongah Park, Nayoung Kim, Sungjin Park, and Geonyeong Ko are with Sogang University, Seoul, Republic of Korea.}%
\thanks{Junho Lee and Changjoo Nam are with Institution2, Seoul, Republic of Korea.}%
\thanks{Corresponding author: Changmin Park (email: cmp9877@gmail.com).}}

\maketitle

\begin{abstract}
In this paper, we propose a knowledge-based POMDP framework for robots that ask humans to verify uncertain state. While modern robotic systems achieve strong autonomy, they still fail due to perception errors, execution failures, and environmental changes, often requiring human supervision. Existing assistance-seeking systems frequently ask for actions, plans, or interventions, which can require users to reason about the robot's belief and future execution. In contrast, our framework represents task knowledge as symbolic facts, maintains a belief over possible worlds, and uses entropy-based confidence to decide when the current belief requires human input. When feedback is needed, the robot asks a targeted state-level question whose answer filters possible worlds and directly reduces planning-relevant ambiguity. We evaluate the proposed framework in simulated waste sorting, real-world tomato harvesting, and a Wizard-of-Oz user study. The results show that state-level verification can preserve task performance while reducing interaction relative to dense supervision, and that its benefits depend on the task structure and the query interface.
\end{abstract}

\begin{IEEEkeywords}
Robotic systems, planning under uncertainty, human-robot interaction.
\end{IEEEkeywords}

\input{section/01_intro}
\input{section/02_related}
\input{section/03_preliminaries}
\input{section/04_method}
\input{section/05_exp_setting}
\input{section/05_exp_system}
\input{section/05_exp_user}
\input{section/06_conclusion}

\section*{Acknowledgement}
This research was supported in part by the National Research Foundation of Korea (NRF) grant funded by the Korea government (MSIT)(No. RS-2024-00461583) and the National Research Foundation of Korea (NRF) grant funded by the Korea government (MSIT) (No. RS-2024-00411007).

\bibliographystyle{IEEEtran}
\bibliography{ref}


\newpage
\onecolumn

\appendices
\input{appendix/00_appx_content}
\input{appendix/01_algorithms.tex}
\input{appendix/02_detailedEXP.tex}
\input{appendix/03_exp.tex}
\input{appendix/04_user_study.tex}

\end{document}
