\section{Related Work}~\label{related}
We review related work on structured task knowledge, planning under uncertainty, and uncertainty-driven human feedback. Table~\ref{tab:comparison} compares representative approaches by their use of interpretable knowledge, symbolic action models, uncertainty-aware planning, human feedback, and system-initiated queries. A circle indicates explicit support, whereas a triangle indicates partial or implicit support without a dedicated symbolic formulation.

\begin{table*}[t]
\caption{Qualitative comparison of related works. A symbolic action model denotes an explicit task-level model of action preconditions and effects.}
\label{tab:comparison}
\centering
\small
\setlength{\tabcolsep}{3pt}
\renewcommand{\arraystretch}{1.5}
\begin{tabularx}{\textwidth}{p{0.30\textwidth}
>{\centering\arraybackslash}X
>{\centering\arraybackslash}X
>{\centering\arraybackslash}X
>{\centering\arraybackslash}X
>{\centering\arraybackslash}X}
\toprule
Related Works
& \makecell{Interpretable\\Knowledge}
& \makecell{Symbolic\\Action Model}
& \makecell{Uncertainty\\Planning}
& \makecell{Human\\Feedback}
& \makecell{System-Initiated\\Query} \\
\midrule
Logic-based knowledge
~\cite{tenorth2012knowledge,liu2020graph,
kunze2014using,hasegawa2023inferring,
mota2021integrated,zhang2024icorpp,daruna2019robocse,
mitrevsk2021ontology,olivares2019review,manzoor2021ontology}
& $\bigcirc$ & $\times$ & △ & $\times$ & $\times$ \\

Symbolic planning
~\cite{fikes1971strips,aeronautiques1998pddl,
helmert2009concise,hoffmann2001ff,
helmert2006fast,correa2024lifted}
& $\bigcirc$ & $\bigcirc$ & $\times$ & $\times$ & $\times$ \\

LLM-based approaches
~\cite{ahn2022can,huang2022inner,singh2023progprompt,liang2023code,ding2023task,
gu2024conceptgraphs,leanza2025conceptbot,singh2025adaptbot,zhouenhancing,xu2024p,
wang2025instructrag,kumar2026open,huang2023voxposer,dai2024optimal,
liu2025delta,paulius2025bootstrapping,quartey2025verifiably}
& △ & △ & △ & $\times$ & $\times$ \\

POMDP-based planning
~\cite{somani2013despot,bai2015intention,cramer2021probabilistic,bravo2019use,
lauri2016exploration,kim2021plgrim,vanegas2016uav,xiao2019objectsearch,
pajarinen2022composition}
& $\times$ & $\times$ & $\bigcirc$ & $\times$ & $\times$ \\

Symbolic uncertainty planning
~\cite{li2026uncertainty,sanner2010symbolic,zhang2015corpp,serrano2021knowledge,
tang2025tru}
& $\bigcirc$ & $\bigcirc$ & $\bigcirc$ & $\times$ & $\times$ \\

Proactive assistance
~\cite{singi2023hula,igbinedion2024learning,zhao2025conformalized,mangalindan2025seek,
shen2024elba,testoni2024asking}
& $\times$ & $\times$ & △ & $\bigcirc$ & $\bigcirc$ \\

KnowNo-style action queries
~\cite{ren2023robots,liang2024introspective,mullen2025lbap}
& $\bigcirc$ & $\times$ & $\bigcirc$ & $\bigcirc$ & $\bigcirc$ \\

\midrule
\textbf{Ours}
& $\bigcirc$ & $\bigcirc$ & $\bigcirc$ & $\bigcirc$ & $\bigcirc$ \\
\bottomrule
\end{tabularx}
\end{table*}

\subsection{Knowledge-Based State and Action Models}~\label{rel:kb}
In robotics, a knowledge base represents task-relevant information in a structured and interpretable form~\cite{brachman2004knowledge,russell1995modern}. Prior work has used symbolic predicates~\cite{fikes1971strips,aeronautiques1998pddl}, temporal logic~\cite{liu2020graph}, ontologies~\cite{mitrevsk2021ontology}, and scene graphs~\cite{johnson2015image,armeni20193d} to describe objects, attributes, relations, goals, and constraints. This interpretability is important because robots can reason over explicit task facts, while users can inspect, correct, or confirm the same facts during interaction.


However, knowledge alone is not sufficient for robot execution. A robot also needs a transition model that specifies which actions are feasible in a state and how those actions change the state. Symbolic planning provides a representative formulation of such transition models through planning languages such as STRIPS~\cite{fikes1971strips}, PDDL~\cite{aeronautiques1998pddl}, and FDR~\cite{helmert2009concise}. In these representations, states are defined by predicates, and actions are defined by preconditions and effects. This structure allows classical planning methods~\cite{hoffmann2001ff,helmert2006fast,correa2024lifted} to compute action sequences over a well-defined symbolic state space. For example, knowing whether an object is \texttt{plastic} or whether a tomato is \texttt{ripe} is not merely a semantic label. These facts change which placement, harvesting, or discarding actions are valid. As shown in Table~\ref{tab:comparison}, classical symbolic planning provides interpretable knowledge and symbolic action models, but it is usually limited in considering partial observability, noisy observations, and uncertain inferred facts.


Knowledge-based robotic systems also use symbolic structure to store observed facts and infer unobserved knowledge from existing information. Logical and relational inference can combine multiple relations and derive plausible hidden states from contextual knowledge~\cite{tenorth2012knowledge,liu2020graph}. For example, robots can infer the likely location of unseen objects from qualitative spatial relations, container-location relations, or place-object co-occurrence knowledge~\cite{kunze2014using,hasegawa2023inferring}. Commonsense reasoning further connects symbolic knowledge with perceptual evidence in partially observable environments~\cite{mota2021integrated,zhang2024icorpp,daruna2019robocse}, while ontologies and type hierarchies support consistent integration and generalization across objects, actions, and task contexts~\cite{mitrevsk2021ontology,olivares2019review,manzoor2021ontology}. These methods help organize uncertain task knowledge, but they usually do not define how uncertainty in a state fact changes action feasibility through an explicit transition model.

Recent work has also used large language models (LLMs) to represent and use task knowledge in more flexible forms, including natural language knowledge and commonsense priors. One line of work uses LLMs directly as planners. These methods generate task decompositions or action sequences and ground them with robot affordances~\cite{ahn2022can,huang2022inner}, programmatic interfaces~\cite{singh2023progprompt,liang2023code}, or execution feedback~\cite{ding2023task}. Other methods enrich this process with scene graphs and open-vocabulary spatial representations~\cite{gu2024conceptgraphs,leanza2025conceptbot}, or with retrieved demonstrations, procedural knowledge, and task constraints~\cite{singh2025adaptbot,zhouenhancing,xu2024p,wang2025instructrag,kumar2026open}. This line is flexible, but action feasibility is difficult to guarantee if the plan itself is produced by the LLM.

Another line uses LLMs to generate formal task specifications, such as PDDL or temporal logic. The generated specification is then solved by off-the-shelf planners, automata, or verification mechanisms~\cite{huang2023voxposer,dai2024optimal,liu2025delta,paulius2025bootstrapping,quartey2025verifiably}. Recent temporal-logic-based systems follow this direction by translating language instructions into LTL or hierarchical temporal-logic specifications~\cite{xu2025nl2hltl2plan,rabiei2025ltlcodegen,wu2025selp,li2025automatic,hu2026llm}. This improves executability, but it inherits the limitation discussed above: the resulting pipeline still provides limited support for uncertainty in observed or inferred state facts. 

Together, these works motivate the axes in Table~\ref{tab:comparison}: interpretable task knowledge, symbolic transition models, uncertainty-aware planning, and human feedback. Interpretability is essential for feedback because users can only verify or correct uncertainty when the robot exposes it as meaningful task facts. Our work focuses on this intersection by maintaining uncertainty over symbolic task facts while using the transition model to evaluate their effect on feasible actions.

\subsection{Planning under Uncertainty}~\label{rel:PlanningUncertainty}
Robotic uncertainty often stems from partial observability, where the full world state is not directly available. POMDPs provide a standard formulation for planning under such uncertainty. We review POMDP planning, belief approximation, and symbolic extensions.

\subsubsection{POMDP}~\label{rel:pu_pomdp}
Unlike deterministic symbolic knowledge-based systems that assume a single world state, POMDPs represent uncertainty as a belief over multiple possible states. In robotic environments, such uncertainty naturally arises from sensor noise, occlusions, incomplete observations, and unexpected state changes. Sequential decision-making under these conditions has been extensively studied within the framework of POMDPs~\cite{somani2013despot,bai2015intention,cramer2021probabilistic,bravo2019use}.


A key distinction between a POMDP and an MDP is the introduction of a belief state, which represents a probabilistic distribution over possible states when the true state cannot be directly observed. Accordingly, a wide range of solution methods have been proposed, including point-based value iteration~\cite{pineau2003point}, online tree search~\cite{ross2008online}, and Monte Carlo tree search (MCTS)~\cite{silver2010monte}.


Despite these advances, effectively representing and updating the belief state remains a fundamental challenge. Since a belief is inherently a continuous distribution over the state space, exact inference is computationally difficult. Moreover, as the state space grows, the belief space expands combinatorially, making inference increasingly intractable. As a result, various approaches have been proposed to approximate the belief state.


\subsubsection{Belief Approximation}~\label{rel:pu_belief_approx}
Studies on belief approximation can be broadly categorized into particle-based and factored approaches. Particle-based methods approximate the belief as a set of sampled states and have been widely adopted due to their natural compatibility with sampling-based online planning~\cite{doshi2005particle, lim2023optimality}. For example,~\cite{silver2010monte} maintains a set of particles as a history-conditioned belief and estimates action values by sampling future trajectories from a generative model without performing exact Bayesian belief updates. Similar sampling-based ideas have also been extended to large and continuous POMDPs, where DESPOT~\cite{somani2013despot} evaluates a limited set of sampled scenarios and POMCPOW~\cite{sunberg2018pomcpow} controls search tree growth in continuous action and observation spaces.



In robotic domains, particle-based belief representations are widely used in localization, navigation, SLAM, object search, and manipulation, where particles encode hypotheses over robot, map, and object states under uncertainty. In navigation,~\cite{lauri2016exploration} combines POMCP with model predictive control to maximize information gain over occupancy-grid maps, while~\cite{kim2021plgrim} uses hierarchical local online POMDP planning for exploration in large unknown environments. Similar representations have also been used for continuous control under uncertainty, including autonomous driving at occluded intersections~\cite{brechtel2014continuous} and UAV collision avoidance or target tracking under partial observability~\cite{bai2011uav,vanegas2016uav}. In object search and manipulation, particles often represent complete scene hypotheses. For example,~\cite{xiao2019objectsearch} samples visible and occluded object configurations for cluttered object search, while~\cite{pajarinen2017multiobject,pajarinen2022composition} uses particle-based scene hypotheses for multi-object manipulation. Collectively, these studies show that particle beliefs provide a flexible approximation for preserving multimodal dependencies among robot, environment, and object states.


In contrast, factored belief representations model the belief by decomposing the state into a set of variables and exploiting their structure~\cite{hansen2000dynamic, feng2001approximate, veiga2014point}. Such approaches have been widely used in structured probabilistic models, including dynamic Bayesian networks and Hidden Markov Models~\cite{eddy1996hidden}, where the state is represented in a factored form. To improve computational efficiency, various approximate inference methods have been proposed to reduce the complexity of belief updates by relaxing dependencies among variables. For example,~\cite{murphy2013factored} approximates belief updates by maintaining a factorized representation while partially accounting for dependencies between variables. This relaxation can be problematic in symbolic planning, where predicates are coupled by action preconditions, effects, and mutual constraints. Particle-based beliefs instead preserve complete state hypotheses, making them better suited to represent dependencies among symbolic facts during planning.


\subsubsection{Symbolic Planning under Uncertainty}~\label{rel:pu_sym}
As described in Section~\ref{rel:kb}, symbolic planning formalisms are interpretable because they describe planning problems through explicit constraints and state transition rules~\cite{ghallab2016automated,lifschitz2019answer}. However, standard predicate-based representations typically assign each fact a binary truth value, making it difficult to directly model observation noise or state uncertainty.

To address this limitation, various approaches have attempted to integrate probabilistic reasoning into logical representations. For example,~\cite{richardson2006markov} assigns weights to logical rules to enable probabilistic inference over uncertain relationships, and~\cite{qu2019probabilistic} combines logical structure with probabilistic reasoning. However, these approaches primarily focus on building inference models, and their high cost in model construction is unsuitable for online decision-making with complex constraints. 


As a result, several studies have explored planning under uncertainty while preserving symbolic structure~\cite{li2026uncertainty,sanner2010symbolic}. For example,~\cite{zhang2015corpp} encodes commonsense knowledge in ASP~\cite{lifschitz2019answer} to construct a prior over possible worlds and integrates it with probabilistic planning~\cite{kurniawati2008sarsop}. However, since the belief is defined over a set of possible worlds, the computational cost increases as the number of states grows. To address this, some works organize possible worlds in a structured manner. For instance,~\cite{serrano2021knowledge} construct a state space tree and a hierarchy of POMDPs based on domain knowledge, reducing complexity by leveraging abstraction. More recently, large language models have been used for belief approximation, as in~\cite{tang2025tru}, which builds a tree of hypotheses and uses LLMs to generate particles in open-ended settings. While these approaches enable more flexible or scalable belief representations, they either depend on predefined hierarchical structures or rely on the quality and consistency of generated hypotheses.


Overall, prior work addresses the uncertainty-aware planning axis in Table~\ref{tab:comparison} while showing that symbolic structure can make uncertain planning more interpretable. However, belief maintenance remains costly if many symbolic hypotheses must be considered. This motivates approaches that focus planning on task-relevant reachable hypotheses rather than maintaining a global belief over all possible worlds. It also raises a complementary question tied to the human-feedback and system-initiated-query axes in Table~\ref{tab:comparison}: when uncertainty remains unresolved, what information should a robot obtain to directly disambiguate competing symbolic states? We next review human feedback and query-based systems that address this question.



\subsection{Human Corrective System}~\label{rel:HCS}
Robots still fail in partially observable environments because uncertainty cannot always be resolved from sensing and planning alone. Human intervention is therefore an important mechanism for correcting errors, resolving ambiguity, and improving robustness~\cite{kelly2019hg,mandlekar2020human}. This corresponds to the human-feedback axis in Table~\ref{tab:comparison}. In human-on-the-loop (HOTL) systems, robots execute tasks autonomously while human operators monitor the system and revise or override decisions when failures occur~\cite{scharre2015introduction,nahavandi2017trusted}.

However, HOTL systems require operators to sustain attention and detect failures during robot operation. To provide effective corrective feedback, operators must first notice that the robot is in an uncertain or erroneous state. Situation awareness research suggests that operators must then understand the current situation, project possible consequences, and determine an appropriate intervention~\cite{endsley2018automation}. This cognitive process can be difficult in repetitive tasks. Operators may experience vigilance decrement because continuous exposure to monotonous monitoring tasks can slow responses and reduce detection accuracy~\cite{davies1982psychology, davies2013human}. Operators may also experience inattentional blindness, in which visible failures are missed if attention is not directed to the relevant event~\cite{mack2003inattentional}. As a result, continuous supervision can increase workload and fatigue~\cite{wong2017workload}. Continuous supervision can also reduce the likelihood that operators detect critical robot failures~\cite{wong2017workload, galster2006managing}.


Prior work has shown that robots can improve task performance, team efficiency, and subjective satisfaction if they proactively provide assistance during human-robot collaboration~\cite{baraglia2017efficient}. This finding suggests that proactive robot behavior can support collaboration by reducing the need for humans to manage every decision or detect every need for intervention. Related help-seeking systems decide when to request expert actions, manual control, or assistance based on policy uncertainty, task difficulty, or trust dynamics~\cite{singi2023hula,igbinedion2024learning,zhao2025conformalized,mangalindan2025seek}. Clarification systems similarly ask questions when model uncertainty is high in embodied task completion or collaborative dialogue~\cite{shen2024elba,testoni2024asking}.


Recent uncertainty-aware query systems further study when a robot should initiate interaction. A representative example is~\cite{ren2023robots} (KnowNo), which uses conformal prediction to form a prediction set over candidate robot actions and asks the user when the set is not sufficiently resolved. Related LLM planning systems extend this direction:~\cite{liang2024introspective} combines retrieval-augmented reasoning with calibrated plan selection, and~\cite{mullen2025lbap} uses uncertainty over candidate plans to decide when the robot should ask for help. These methods provide principled mechanisms for system-initiated queries. However, their queries are typically action-level choices, expert interventions, or clarifications among candidate plans. Such queries can require users to infer the current state of robot and understand how candidate actions affect future execution. This shifts part of the situation-awareness burden to the user where the user must interpret the current state, project action consequences, and choose an intervention. Our framework instead asks users to verify symbolic variables grounded in the knowledge base, so the requested feedback is stated as a task-level fact rather than an action decision. We view this as a complementary interaction primitive: the robot keeps the planning responsibility, while the user provides targeted evidence about the world state.


This difference in query content changes what users must understand and decide during interaction. Thus, operator burden is also relevant if analyzing system-initiated corrective interaction. Existing studies mainly report task success, uncertainty calibration, and query efficiency. However, workload can affect task performance and intervention quality in automated systems that involve human operators~\cite{murata2000ergonomics,borragan2017cognitive,rajavenkatanarayanan2019towards}.


Motivated by this consideration, we include operator workload as a user-facing measure alongside task performance. In our interaction structure, the robot monitors its belief uncertainty and asks for corrective feedback if additional information is useful. Users provide targeted input at system-identified moments rather than continuously monitoring for failures. This positions our system in Table~\ref{tab:comparison} as combining human feedback and system-initiated queries with interpretable symbolic knowledge, action constraints, and planning under uncertainty.
