\section{Planning Algorithms}~\label{appx:algorithms}

This appendix provides the detailed pseudocode for the POMCP-based search routines described in Sec.~\ref{method:PM}.

\normalem
\subsection{POMCP Search with Applicable Actions}~\label{appx:alg_search}
Alg.~\ref{alg:search} summarizes the root search procedure. The search samples states from the current belief when particles are available, falls back to the committed knowledge state when the belief is empty, and repeatedly calls the simulation routine until the computation budget is exhausted. The final action is selected from actions applicable to the current knowledge state.

\begin{algorithm}[h]
\caption{POMCP Search with Applicable Actions}
\label{alg:search}
\textbf{Input}: belief $b$ \\
\textbf{Output}: selected action $a \in \mathcal{A}$
\BlankLine

\Proc{\Search{$b$}}{
    $h \gets$ root history\\
    $s^{K} \gets knowledge(b)$\\
    
    \Repeat{\Timeout}{
        \eIf{$B(h) \neq \emptyset$}{
            sample $s \sim B(h)$ \label{alg_search:sample}\\
        }{
            $s \gets s^{K}$\\
        }
        
        \Simulate{$s, h, 0$} \label{alg_search:simulate}\\
    }
    $a \gets$ \SearchBest{$h, s^{K}, \textnormal{false}$}  \label{alg_search:search_best}\\
    \KwRet $a$ \\
}
\end{algorithm}

\subsection{POMCP Simulation with Applicable Actions}~\label{appx:alg_simulate}
Alg.~\ref{alg:simulate} describes how simulations are constrained by symbolic action applicability. When a new history node is expanded, only actions whose preconditions hold in the sampled symbolic state are inserted into the search tree. The generative model then samples the next state, observation, and reward while preserving the standard POMCP value-update structure.

\begin{algorithm}[h]
\caption{POMCP Simulation with Applicable Actions}
\label{alg:simulate}
\textbf{Input}: state $s$, history $h$, depth $depth$ \\
\textbf{Output}: simulated return $R$
\BlankLine

\Proc{\Simulate{$s, h, depth$}}{
    \If{$\gamma^{depth} < \epsilon$}{
        \KwRet $0$\\
    }

    \If{there is no $a\llbracket s \rrbracket \in \mathcal{A}$}{
        $N(h) \gets N(h) + 1$\\
        \KwRet $0$\\
    }

    \If{$h \notin T$}{
        \ForEach{$a\llbracket s \rrbracket \in \mathcal{A}$ \label{alg_simulate:applicable}}{
            $T, N(ha), V(ha) \gets T \cup \{ha\}, 0, 0$ \label{alg_simulate:tree_expand}\\
        }
        $N(h) \gets N(h) + 1$\\
        \KwRet \Rollout{$s, depth$} \label{alg_simulate:rollout}\\
    }

    $a \gets$ \SearchBest{$h, s, \textnormal{true}$} \label{alg_simulate:search_best}\\
    sample $(s^\prime, o, r)$ from simulator $\mathcal{G}(s, a)$ \label{alg_simulate:simulate}\\

    $R \gets r + \gamma \cdot$ \Simulate{$s^\prime, hao, depth + 1$}\\

    $B(h)\gets B(h) \cup \{s\}$\\
    $N(h) \gets N(h)+1$\\
    $N(ha) \gets N(ha)+1$\\
    $V(ha) \gets V(ha) + \frac{R - V(ha)}{N(ha)}$\\

    \KwRet $R$\\
}
\end{algorithm}

\subsection{Action Selection and Rollout}~\label{appx:alg_selection}
Alg.~\ref{alg:selection} specifies the shared action-selection routine used during tree search and rollout. Tree actions are selected using either the UCB criterion or the current value estimate, whereas rollout actions are sampled uniformly from applicable actions. This keeps both planning and rollout consistent with the symbolic transition model.

\begin{algorithm}[h]
\caption{Action Selection and Rollout}
\label{alg:selection}
\textbf{Input}: history $h$, state $s$
\BlankLine

\Proc{\SearchBest{$h, s, use\_ucb$}}{
    $\mathcal{C} \gets \{a \mid a\llbracket s \rrbracket \in \mathcal{A},\ ha \in T\}$\\
    
    \If{$\mathcal{C} = \emptyset$}{
        \KwRet $\emptyset$\\
    }

    \eIf{$use\_ucb$}{
        \KwRet $\arg\max_{a \in \mathcal{C}} V(ha) + c \cdot \sqrt{\frac{\log N(h)}{1 + N(ha)}}$\\
    }{
        \KwRet $\arg\max_{a \in \mathcal{C}} V(ha)$\\
    }
}
    
\BlankLine

\Proc{\Rollout{$s, depth$}}{
    \If{$(\gamma^{depth} < \epsilon \lor \gamma = 0) \land depth > 0$}{
        \KwRet $0$\\
    }

    \If{there is no $a\llbracket s \rrbracket \in \mathcal{A}$}{
        \KwRet $0$\\
    }

    $a \sim \mathrm{Uniform}(\{ a \mid  a\llbracket s \rrbracket \in \mathcal{A}\}  )$ \label{alg_rollout:uniform}\\
    sample $(s^\prime, o, r)$ from simulator $\mathcal{G}(s, a)$ \label{alg_rollout:simulator}\\

    \KwRet $r + \gamma \cdot$ \Rollout{$s^\prime, depth + 1$}\\
}
\end{algorithm}
