\section{Additional Experimental Results}~\label{appx:exp}

The main text reports aggregate results for the threshold experiment and policy comparison. This appendix summarizes the design logic behind these aggregate values.

\paragraph{Threshold experiment.}
\cp{The threshold $\tau$ controls when belief confidence is considered sufficient for autonomous execution. Low thresholds allow the robot to commit to a state estimate with little feedback, which reduces query frequency but can leave task-relevant uncertainty unresolved. Higher thresholds request more feedback and concentrate the belief before downstream actions are selected. Table~\ref{tab:sys_tau} shows that this effect is domain dependent. Waste sorting improves sharply once a small amount of category uncertainty is resolved, whereas tomato harvesting requires a higher threshold because uncertainty propagates through navigation, detection, picking, scanning, and placement decisions. The highest threshold does not always improve performance: in tomato harvesting, success decreases from $82.5\%$ at $\tau=0.8$ to $76.0\%$ at $\tau=1.0$ while the query rate reaches $1.00$. We therefore interpret $\tau=1.0$ as an over-querying regime rather than as a strictly better operating point.}

\paragraph{Policy comparison.}
\cp{The policy comparison in Table~\ref{tab:system_eval} uses $\tau=0.8$ for \textbf{Ours}. \textbf{All} represents an upper-interaction baseline that asks whenever a query is available. \textbf{No} represents fully autonomous execution without corrective feedback. \textbf{Random} uses the same state-query interface but selects questions uniformly at random. Thus, the comparison separates three effects: availability of human information, timing of feedback, and information gain of the selected hypothesis. Random querying is relatively effective in waste sorting because the task horizon is short and many category questions can help the next placement decision. In tomato harvesting, however, random querying fails because useful information must be requested at specific stages of a longer dependent workflow. This contrast clarifies why the information-gain criterion matters most when uncertainty can affect several later actions.}

\paragraph{Domain difference.}
Waste sorting contains short pick-and-place sequences and requires correct category assignment before placement. Tomato harvesting contains longer action chains in which ambiguous tomato state estimates affect later scan, place, and discard decisions. Consequently, resolving belief errors at the right moment has greater leverage in tomato harvesting, while waste sorting gives shorter opportunities for uncertainty to propagate.

\paragraph{KnowNo baseline implementation.}
\cp{For the action-query baseline, we use the same domain scenarios, task dynamics, execution limits, and scene randomization protocol as the other policy baselines. The KnowNo implementation uses GPT-4o with the structured prompt version used in the main experiments, conformal threshold $\hat{q}=0.92$, and scoring temperature $3.0$. The prompts include domain-specific action roles and few-shot examples, and generated options are constrained to executable action formats in the corresponding domain. At each decision point, KnowNo forms a prediction set over candidate next actions; when action-level uncertainty remains, the user-facing query asks the operator to select among action options rather than to verify a symbolic state predicate. This setup follows the action-query framing of KnowNo while keeping the environment, transition model, and maximum step budget matched to the state-query baselines.}

\paragraph{Scalability aggregation.}
\cp{The scalability results use only \texttt{scene\_06.yaml}--\texttt{scene\_10.yaml}, which increase each domain from four task objects to six task objects. Each scaled scene is evaluated with $40$ randomized episodes, for $200$ episodes per domain. The scaled runs use the proposed query policy with $\tau=0.8$, a maximum episode length of $90$ steps, and $800$ maximum belief particles. The reported runtime and search statistics are episode or step means over these scaled runs; the original columns in Table~\ref{tab:sys_scale} reuse the standard four-object \textbf{Ours} results under the same threshold.}
